# mHealthR package

#### Author: [Qu Tang](http://qutang.github.io)

#### Version: `r library(mHealthR);packageVersion(pkg = "mHealthR")`

---

## Intro

This package is used to *validate*, *read*, *write*, *plot*, *convert* and *manipulate* annotated mobile health data (such as physical and phisiological sensor data) store in [mhealth specification](https://qutang.github.io/project/mhealth-specification/).

## Features

* Work with dataframe only

* Minimal API

* String based iput argument

## Installation

```{r, eval=FALSE, include=TRUE}
# install.packages("devtools")
devtools::install_github("qutang/mHealthR")
```

## Examples

### Insightful validation

#### 1. Validate filename
```{r, eval=FALSE, include=FALSE}
library(mHealthR)
```

```{r eval = TRUE, echo=TRUE, message=TRUE, warning=FALSE, comment=NA, INCLUDE=TRUE}
result = mhealth.validate("name_type.iD.2015-13-12-12-32-12-222-M0500.annotation.csv.gz", file_type = "sensor")
```

#### 2. Validate dataframe
```{r eval = TRUE, echo=TRUE, message=TRUE, warning=FALSE, comment=NA, INCLUDE=TRUE}
result = mhealth.validate(mtcars[1:2], file_type = "sensor")
```

