---
title: "mhealth object"
author: "Qu Tang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
library(mHealthR)
```

`mhealth` named list stores constants in a hierarchical structure. You can run `str(mhealth)` to display them compactly.

## mhealth$filetype

Use `mhealth$filetype` sub list to query available file types which are often required for other `mhealth` functions.
```{r, echo=FALSE, comment=NA}
str(mhealth$filetype)
```

As an example,
```{r, eval=FALSE}
# validate sensor file
mhealth.validate(filename, mhealth$filetype$sensor)
```

## mhealth$format

Use `mhealth$format` sub list to query datetime and other format for mhealth specification.
```{r, echo=FALSE, comment=NA}
str(mhealth$format)
```

## mhealth$example

Use `mhealth$example` sub list to examples of filenames or csv files for mhealth specification.

### Examples of filename (`mhealth$example$filename`)
```{r, echo=FALSE, comment=NA}
str(mhealth$example$filename)
```

### Examples of csv format (not available)


